---
title: "package 'dragDBI'"
authors: "Veronika Prieložná,Petr Pyszko <https://orcid.org/0000-0002-3743-7201>"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"package 'dragDBI'"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Introduction
The dragDBI package....

### Installation
The current release (1.0) of the package can be installed from GitHub... pomocí příkazů níže. Homepage je na tomto odkaze
[https://github.com/VeronikaPrielozna/dragDBI](https://github.com/VeronikaPrielozna/dragDBI)..

```{r, eval = FALSE}
install.packages("devtools")
library("devtools")
install_github("VeronikaPrielozna/dragDBI")
```

### Data required

### Input format
Napsat, ze musi byt takova a takova data. Priklad dat can be seen by accessing the built-in 'Data' dataset

```{r}
# load library
library("devtools")

# show the format of built-in dataset

```

### Functions
```{r}
# library

library(dragDBI)

```


```{r}
# Uploading user-defined DBI checklist. Saved as DBI_UD. 

DBI_UD<-LoadDBI(attrib=F) 

```

```{r}
#          Species DBI
#  Aeshna affinis   5
# Aeshna caerulea   9
#   Aeshna cyanea   0
#  Aeshna grandis   1
#   Aeshna juncea   0
#    Aeshna mixta   1
#         ...       .

```

```{r}
# Uploading data containing species of Central Europe. Saved as x_CE.  

x_CE<-LoadData(attrib = F) 

```

```{r}
#                  X Sam1 Sam2 Sam3 Sam4 Sam5
#      Aeshna mixta    0    1    0    0    0
# Aeshna subarctica    1    4    1    0    0
#   Aeshna isoceles    3    6    7    1    0
#    Anax imperator    0    0    0    2    4
#   Anax parthenope   14    0    0    0   23

```

### Individual index functions
```{r}
# dat priklady tech unfkci pro ty jednotlive indexy.

```

### Reporting problems
The package has been tested fairly extensively...

### Source of the information about the indices calculated


```{r setup}
library(dragDBI)
```

